Analysis of Fault Localization Techniques on REST APIs

### 2024-05-28 CS563-Project/Paper/paper.tex
update metrics

There are several metrics that can be used to evaluate how effective FL techniques are at localizing REST API faults. In this research, two primary metrics to consider are \textbf{Top-k accuracy}, and \textbf{EXAM}.

     \textbf{Top-k accuracy:} This metric measures the percentage of faulty statements found within the top k positions of the ranking generated by an FL technique. The ranking positions are based on how likely each statement is considered faulty according to the fault localization algorithm. This metric is useful for evaluating how effective FL techniques are at localizing faults. In this research, several values of k are used to measure the FL technique's performance, such as top-1, top-3, top-5, and top-10.
    \\
    This metric measures the percentage of times the actual faulty statements are within the top $k$ positions of a ranked list produced by the fault localization technique. Mathematically, it is expressed as:
    \[
    \text{Top-k} = \frac{\text{ \#faults found in top } k \text{ positions}}{\text{Total number of faults}} \times 100\%
    \]
    This metric evaluates the effectiveness of fault localization techniques by their ability to rank the actual faulty statements highly on the list. Commonly used values for $k$ include 1, 3, 5, and 10.
    \\

    \textbf{EXAM score:}  This metric is defined as the percentage of the total statements a developer needs to examine before finding the fault location. A low EXAM score indicates that the fault localization technique was able to rank faulty statements highly, reducing the amount of code that needs to be inspected. This reflects an effective fault localization technique that quickly directs developers to the most likely faulty areas. However, the EXAM score does not account for multiple faults, limiting its ability to measure the effectiveness of an FL technique for multiple faults.

    The EXAM score is calculated as the percentage of the code that must be examined until the first occurrence of a fault is encountered. It is defined as:
    \\
    \[
    \text{EXAM Score} = \frac{\text{Position offault in the ranked list}}{\text{Total number of statements}} \times 100\%
    \]
    A lower EXAM score indicates a more effective fault localization technique, as it suggests that fewer statements need to be inspected before finding the fault. This metric is particularly useful for assessing the efficiency of a technique in directing developers quickly to the likely fault locations.
    \\ \\
    \textbf{Preicision}: This metric measures the fraction of actually faulty statements out of the total reported faulty statements. It provides a measurement indicating how well an FL technique can localize faults. However, it doesn't capture an FL technique's capability to localize all faults.
    \\

>>>>

There are several metrics that can be used to evaluate how effective FL techniques are at localizing REST API faults. In this research, two primary metrics to consider are \textbf{Top-k Accuracy}, and \textbf{EXAM}.

     \textbf{Top-k Accuracy:} This metric measures the percentage of actual faulty statements found within the top k position of the ranking generated by an FL technique. The ranking positions are based on how likely each statement is considered faulty according to the fault localization algorithm. This metric is useful for evaluating how effective FL techniques are at localizing faults. In this research, several values of k are used to measure the FL technique's performance, such as top-1, top-5, and top-10.
    \\
    This metric measures the percentage of times the actual faulty statements are within the top $k$ positions of a ranked list produced by the fault localization technique. Mathematically, it is expressed as:
    \[
    \text{Top-k} = \frac{\text{ \#faults found in top } k \text{ positions}}{\text{Top k positions}} \times 100\%
    \]
    This metric evaluates the effectiveness of fault localization techniques by their ability to rank the actual faulty statements highly on the list. 
    \\

    \textbf{EXAM score:}  This metric is defined as the percentage of the total statements a developer needs to examine before finding the fault statement. A low EXAM score indicates that the fault localization technique was able to rank faulty statements highly, reducing the amount of code that needs to be inspected. This reflects an effective fault localization technique that quickly directs developers to the most likely faulty areas. However, the EXAM score does not account for multiple faults, limiting its ability to measure the effectiveness of an FL technique for multiple faults.

    The EXAM score is calculated as the percentage of the code that must be examined until the first occurrence of a fault is encountered. It is defined as:
    \\
    \[
    \text{EXAM Score} = \frac{\text{Number of statements before fault}}{\text{Total number of ranked statements}} \times 100\%
    \]
    A lower EXAM score indicates a more effective fault localization technique, as it suggests that fewer statements need to be inspected before finding the fault. This metric is particularly useful for assessing the efficiency of a technique in directing developers quickly to the likely fault locations.
    \\ \\
